Simulations log

### 2020-04-26 manuscript/drafts/manuscript.Rmd
update methods section

---
title: "Manuscript drafts"
author: "Gerbrich Ferdinands"
date: "22/04/2020"
output:
  word_document: default
  pdf_document:
    citation_package: biblatex
bibliography: asreview.bib
---

@@

<!-- assist the reviewer in the screening process -->
<!-- Several studies have proposed active learning models for screening prioritization -->
Recent studies have demonstrated the effectiveness of screening prioritization by means of active learning models [@Yu2019; @Yu2018; @Miwa2014].
Active learning is when the model can iteratively improve its predictions by allowing the model to choose the data from which it can learn [@Settles2012].
Active learning has proven to be an efficient strategy in large datasets where labels are scarce, which makes identifying relevant publications an ideal candidate for such models.  
When applied in the screening process, an active learning model can iteratively improve its relevancy predictions by interacting with the reviewer.
The model decides which publication it wants the reviewer to screen next, who then provides the model with a label ('relevant', 'irrelevant'). 
In this active learning cycle, the model can incrementally improve its predictions on the relevancy of the remaining unlabeled publications. 
Based on previous labelling decisions by the reviewer, the model constantly reorders the remaining publications in the dataset.

@@

<!-- The tool is generic such that any researcher can adjust modules to increase efficiency in this field.   -->

 <!-- [@OConnor2019] -->

@@

@@

#### summarise models used
#### propose pipeline 
##### and specific components?

#### summarise datasets tested
\
\

## Background
[@OMara-Eves2015] literature review

[@Yu2018a], [@Yu2019] simulated 32 svm classifiers, on software engineering. 
A popular classifier is SVM. succes with HUTM (fastread), uncertainty, mix of weighting and agressive undersampling, 
In terms of Yu et al, we adopt .CT.

@@

Goal: evaluate performance of different models of the ASReview tool. 
The screening process is simulated using ASReview, seeing if the original inclusions replicate. 
What would happen if the citation screening would have been performed using asreview? 
All datasets accompanying the systematic reviews are openly published. 
We built several machine learning models to perform automated systematic reviews, 
who are then applied on existing systematic reviews.

@@

##### indicating the structure of the writing)
principle findings:

@@

automatically (by machine learning techniques)
In the current study we focus on the effectiveness of different machine learning models in reducing workload in the citation screening process. 
Assisting the reviewer. Combining various machine learning techniques. 
Combining recent insights on, we propose ASReview.
Approaching the citation screening phase as a classfication task,
The benefit is that ASReview is dynamic, user can decide
open source, multiple classifiers and other settings,

The current study focus is on reducing workload by prioritizing the most relevant abstracts. Presenting the abstracts orders the abstracts by likelihood of relevance, e.g. th
The reviewer sees the most relevant abstracts first, 
If the model performs well all relevent abstracts will be seen much earlier than when abstracts are read at a random order.

@@

#### Technical details
So you might wonder, how does such an algorithm actually work? Active learning strategy, starting with a pool of unlabeled abstracts (U). The reviewer starts labeling some instances in U, creating L. The algorithm utilizes L to predict labels for all abstracts (classifier), by using a set of features from the papers called X, for example the text in the abstract (feature extraction method). Now, it made an initial classification. The algorithm now aims to improve its classification by which paper from U will be presented to the reviewer next. By labeling the next paper, the reviewer provides the algorithm with new information which the algorithm uses to update its prediction.

We approach asr as a classification problem: 
All papers obtained in the systematic search form a pool of instances x. 
All instances x need to be classified, e.g. we want to give them a label y. 
all x are now part of U,.
Binary classification, either inclusion or exclusion. 
We want to classify based on some features from the instances $x$, feature vector $\mathbf{X}$.

By starting of with L, the algorithm utilizes characteristics of X to predict labels in U.

We want to classify the papers in 
Where the whole collection of papers in the systematic search form a pool of instances x, with unknown label y. 
<x,y>. 
```
input:  
    a pool of unlabeled abstracts $\mathcal{U}$ 
    oracle labels a few initial papers, from $\mathcal{U}$, $\mathcal{L}$,

```
- pool unlabeled abstracts $\mathcal{U}$ 
- labeled data set $\mathcal{L}$, 
- instance $x$, label $y$

- utility measure $\phi_A(\cdot)$
- $x^*_A$ best query instance according to $\phi_A(\cdot)$

Now there are a few technical details. Many different versions of such algorithms exist. Many of such algorithms have been described in the active learning literature and have been applied in the systematic reviewing process.  Not exhaustive, but the algorithm can apply many different strategies to arrive at its predictions, which can be divided in following parameters: classifier, feature extraction strategy, balancing, query strateg y.

Then if we still have time left we explore the effect of another feature extraction method, namely doc2vec. This might possibly increase performance as it performs better at grasping structure/hidden relations/hierarchy between words in the texts. So, it could be interesting in more ‘fuzzy’ research areas. A downside is that it takes more computing time.

Then if there’s even more time we might want to compare a different balance strategy.

@@

models are designed in a 'realistic' way (you have some inclusions)

#### Assumptions 
1) decisions of the original SR are **ground truth** (benchmark) (oracle)

The inclusion rate is ... data is imbalanced. 
what is the philosophy
False negatives must be avoided ... 
The cost of a false negative outweighs the cost of a false positive. 
Note that we assume the oracle/original user to hold the truth. 
This is of course not always the case.

@@

RQ1 - what are good classifiers 
RQ2 - what are good optimization strategies

\newpage
# Methods
This study was approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendement under study 20-104.

All simulations were run using through cartesius EINF-156

Performance of several machine learning models was demonstrated on six systematic review datasets.  
study design: retrospective

## Models 
_x_ machine learning models ($M$) were built. 
The models consist of multiple components, of which the classifier and the feature extraction strategy varied over the models.

#### Classifiers
Every model applies a classifier $c$ to predict the relevance of publications in the data. 
The classfiier predicts the class of a publication in the dataset expediting a training dataset $\mathcal{L}$,
predicts the class of an instance given input features $\mathbf{X}$

Logistic Regression (LR) - L2-regularized logistic regression. 
Logistic models the posterior directly, naive bayes has higher bias but lower variance, 
logistic might perform better when trainign set increases. [@Ng2002]
Naive Bayes (NB) - Naive Bayes assumes all features are independent given the class value. This is obviously not the case but still the algorithm performs impressively [@Zhang2004]. Especially at ... tasks.

Random Forests (RF) is where a large number of decision trees are fit on bootstrapped samples of the original data. All trees cast a vote on the class, which are aggregated into a class prediction for each input $\mathbf{X}$ [@Breiman2001].

Support Vecor Machine (SVM) - finds a multidimensional hyperplane to separate classes.
[@Tong2001]

#### Word representation 
To predict the class of a publication class (e.g. whether a publication should be included or excluded), the classifier uses information from the publications in the dataset. 
Examples of such information are titles and abstracts. 
However, the classifier cannot predict the publication class from titles and abstracts as they are. 
Their textual content to needs to be mapped to feature vectors. 
This process of numerically representing textual content is called 'word embeddings'.

#### Fixed components  
All models $M$ apply the same query strategy of certainty sampling, in which the presented publication is always the one of which the model is most certain for it to be relevant.

## Datasets
Six Systematic Reviews from various research areas were used to simulate the automated systematic review process. Data were preprocessed from the original source into a test dataset, containing all publications obtained in the systematic search. The test datasets are labelled indicating the relevant and irrelevant publications. Using these labels, a computer simulation of an automated systematic review can be performed on the systematic review data.

@@

## Simulations
To demonstrate the models, simulations are performed of the models on six original systematic reviews.  
With the labeled datasets, the systematic review can be reproduced but with now using a machine learning model to optimize the reviewing process.

The initial training set of the active learning model in the simulation is one prior included publication and one prior excluded publication, randomly sampled from the data. 
This demonstrates a 'worst case scenario' where the reviewer has minimal prior knowledge on publications in the data. 
For this simulations there is no need for a human reviewer since the labels in the data can be queried. 
The oracle is not the reviewer but the labels in the data. 
The model retrains every time after a label is provided by the oracle. 
The simulation ends when all publications in the dataset have been queried.

To account for variance, every simulation is repeated for 15 trials $t$.

#### measures
#### comparison over conditions

@@

#### Performance metrics 
For each model, 
Several metrics are used to compare performance of different models over datasets,

? How to compare outcomes of 3 different optimization strategies?

>>>>

---
title: "Manuscript drafts"
author: "Gerbrich Ferdinands"
date: "22/04/2020"
output:
  pdf_document:
    citation_package: biblatex
  word_document: default
bibliography: asreview.bib
---

@@

<!-- assist the reviewer in the screening process -->
<!-- Several studies have proposed active learning models for screening prioritization -->
Recent studies have demonstrated the effectiveness of screening prioritization by means of active learning models [@Yu2019; @Yu2018; @Miwa2014].
Active learning is when the model can iteratively improve its predictions by allowing the model to choose the data from which it can learn [@Settles2012]. Active learning has proven to be an efficient strategy in large datasets where labels are scarce, which makes identifying relevant publications an ideal candidate for such models. When applied in screening prioritization, an active learning model can decide which publication it wants the reviewer to screen next. Based on the reviewers screening decision ('relevant', 'irrelevant'), the model can incrementally improve its relevancy predictions on the remaining publications, and again select the next publication to be screened.

@@

<!-- The tool is generic such that any researcher can adjust modules to increase efficiency in this field.   -->
 <!-- [@OConnor2019] -->

@@

--- 
## Technical details
In this section, the workings of an active learning model for screening prioritization will be explained in more detail.

### Active learning cycle
Active learning has proven to be an efficient strategy in large datasets where labels are scarce, which makes identifying relevant publications an ideal candidate for such models.  
The goal of the technique is to identify the sparse relevant publications as early as possible / present for labelling.
There is a lot of data, but not a lot of labels.

When applied in the screening process, an active learning model can iteratively improve its relevancy predictions by interacting with the reviewer.
The model decides which publication it wants the reviewer to screen next, who then provides the model with a label ('relevant', 'irrelevant'). 
In this active learning cycle, the model can incrementally improve its predictions on the relevancy of the remaining unlabeled publications. 
Based on previous labelling decisions by the reviewer, the model constantly reorders the remaining publications in the dataset.

All publications obtained in the search $x$ form a pool of unlabelled instances $\mathcal{U}$. 
To conduct a systematic review the reviewer needs to identify which publications are relevant, 
The reviewer starts labeling some instances in $\mathcal{U}$, creating labeled data set $\mathcal{L}$.
This is the starting point for the active learning model.
The model trains a model who predicts

- instance $x$, label $y$
- utility measure $\phi_A(\cdot)$
- $x^*_A$ best query instance according to $\phi_A(\cdot)$

```
input:  
    a pool of unlabeled abstracts $\mathcal{U}$ 
    oracle labels a few initial papers, from $\mathcal{U}$, $\mathcal{L}$,

```

All instances x need to be classified, e.g. we want to give them a label y. 
Binary classification, either inclusion or exclusion. 
we start out with a pool of unlabelled abstracts U.

The model utilizes L to predict labels for all abstracts (classifier). (training)
a new paper is selected (query) the one that is most likely to be relevant. & queried 
The reviewer is asked to label the query (relevant, irrelevant), which is then added to the training set. 
Now the model can update in (retraining) its predictions based on the new training dataset. This is caled retraining. 
The cycle starts over again.. 
As the cycle repeats itselfs, labeled dataset grows, predicitons improve hopefully and soon (or sooner than at random) the relevant publications will we identified. s

This is done by using a set of features from the papers called X, for example the text in the abstract (feature extraction method). Now, it made an initial classification. The algorithm now aims to improve its classification by which paper from U will be presented to the reviewer next. By labeling the next paper, the reviewer provides the algorithm with new information which the algorithm uses to update its prediction.

We want to classify based on some features from the instances $x$, feature vector $\mathbf{X}$.

By starting of with L, the algorithm utilizes characteristics of X to predict labels in U. 
We want to classify the papers in 
Where the whole collection of papers in the systematic search form a pool of instances x, with unknown label y. 
<x,y>.

#### details: features, balance, ... / known issues. 
Now there are a few technical details. Many different versions of such algorithms exist. Many of such algorithms have been described in the active learning literature and have been applied in the systematic reviewing process.  Not exhaustive, but the algorithm can apply many different strategies to arrive at its predictions, which can be divided in following parameters: classifier, feature extraction strategy, balancing, query strateg y.

## Models 
_x_ active learning models ($M$) were built. 
The models consist of multiple components, of which the classifier and the feature extraction strategy varied over the models.

#### Classifiers

Every model applies a classifier $c$ to predict the relevance of publications in the data. 
The classifier predicts the class of a publication in the dataset expediting a training dataset $\mathcal{L}$,
predicts the class of an instance given input features $\mathbf{X}$

#### Word representation 
For a model to be able to predict relevancies, the title and abstract of the publications need to be represented numerically. 
To predict the class of a publication class (e.g. whether a publication should be included or excluded), the classifier uses information from the publications in the dataset. 
Examples of such information are titles and abstracts. 
However, the classifier cannot predict the publication class from titles and abstracts as they are. 
Their textual content to needs to be mapped to feature vectors. 
This process of numerically representing textual content is called 'word embeddings'.

#### Fixed components  
Utility measure / query strategy 
All models $M$ apply the same query strategy of certainty sampling, in which the presented publication is always the one of which the model is most certain for it to be relevant.

we explore the effect of another feature extraction method, namely doc2vec. This might possibly increase performance as it performs better at grasping structure/hidden relations/hierarchy between words in the texts. So, it could be interesting in more ‘fuzzy’ research areas. A downside is that it takes more computing time.

@@

# Methods
Several active learning models where developed with the goal of identifying the sparse relevant publications early as possible.
The aim of this study was to assess performance of screening prioritization by several active learning models on increasing efficiency in title and abstract screening in six systematic reviews, compared to screening at random order/in the conventional process. 
Model performance was demonstrated by performing a simulation on six systematic review datasets from various research areas.

To evaluate  retrospective analysis / simulation
various areas for generalizability

## Active Learning Models 
The 7 active learning models tested differ on the classifier and feature extraction they use. 
Four classifiers and two feature extraction strategies were tested, leading to 7 models* *(nb doesn't do d2v)
The performance
 - Naive Bayes + TF-IDF
 - Random Forest + TF-IDF 
 - Support Vector Machine + TF-IDF
 - ...

Logistic Regression (LR) - L2-regularized logistic regression. 
Logistic models the posterior directly, naive bayes has higher bias but lower variance, 
logistic might perform better when trainign set increases. [@Ng2002]
Naive Bayes (NB) - Naive Bayes assumes all features are independent given the class value. This is obviously not the case but still the algorithm performs impressively [@Zhang2004]. Especially at ... tasks. 
Random Forests (RF) is where a large number of decision trees are fit on bootstrapped samples of the original data. All trees cast a vote on the class, which are aggregated into a class prediction for each input $\mathbf{X}$ [@Breiman2001]. 
Support Vecor Machine (SVM) - finds a multidimensional hyperplane to separate classes.
[@Tong2001]

The following were fixed over models:

## Simulation study
To demonstrate the models, simulations are performed of the models on six original systematic reviews. ** asreview has a nice simulation mode. 
The models were applied on data from existing systematic reviews.

The screening process was simulated by

For this simulations there is no need for a human reviewer since the labels in the data can be queried. 
the label column acts as the oracle.
The oracle is not the reviewer but the labels in the data.

The model retrains every time after a label is provided by the oracle. 
The simulation ends when all publications in the dataset have been queried.

#### Assumptions 
1) decisions of the original SR are **ground truth** (benchmark) (oracle)
The initial training set of the active learning model in the simulation is one prior included publication and one prior excluded publication, randomly sampled from the data. 
This demonstrates a 'worst case scenario' where the reviewer has minimal prior knowledge on publications in the data. this is realistic / lower bound.

To account for variance, every simulation is repeated for 15 trials $t$. 
study assumptions:

- simulation mode 
- assumptions (prior knowledge etc, oracle = reviewer).

#### measures
#### comparison over conditions 
The inclusion rate is ... data is imbalanced. 
what is the philosophy
False negatives must be avoided ... 
The cost of a false negative outweighs the cost of a false positive. 
Note that we assume the oracle/original user to hold the truth. 
This is of course not always the case.

#### Data selection & preprocessing
various datasets is necessary cause it is difficult to compare models accross datasets but also model performance is very data dependent!

Six systematic reviews from various research areas were used to simulate the automated systematic review process. Data were preprocessed from the original source into a test dataset, containing all publications obtained in the systematic search. The test datasets are labelled indicating the relevant and irrelevant publications. Using these labels, a computer simulation of an automated systematic review can be performed on the systematic review data.

### How will results be analysed/performance will be evaluated? 
how is 'good' performance defined/quantified?

metrics used: 
#### Performance metrics 
For each model, 
Several metrics are used to compare performance of different models over datasets,

? How to compare outcomes of 3 different optimization strategies? 
---

All datasets accompanying the systematic reviews are openly published. 
This study was approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendement under study 20-104.
Simulations were carried out using ASReview ...,
Statistical analyses were performed using R version ... 
All simulations were run using through cartesius EINF-156

\newpage
## Background
[@Yu2018a], [@Yu2019] simulated 32 svm classifiers, on software engineering. 
A popular classifier is SVM. succes with HUTM (fastread), uncertainty, mix of weighting and agressive undersampling, 
In terms of Yu et al, we adopt .CT.

@@

@@

@@

@@

@@

@@

@@

@@

### 2020-04-26 simulation_study/simulation/README.Rmd
update methods section

# transfer sctd's later!(3)
noquote(transfer("one", condition[c(1, 2,4,7,8,9)], seed = TRUE))
# ace: scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/SCTD/ace /Volumes/Gerbrich/asreview/simoutput/one_seed/SCTD

>>>>

# transfer sctd's later!(3)
noquote(transfer("one", condition[c(1,2,3,4,7,8,9)], seed = TRUE))
# ace: scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/SCTD/ace /Volumes/Gerbrich/asreview/simoutput/one_seed/SCTD

```{r}
seed_virus <- createLines(condition[c(1, 2, 3,4,7,8,9)], "virus", "one", seed = TRUE) %>%
  noquote()
names(seed_virus) <- c("8125572", "8125573", "8125574", "8125575", "8125581", "8125582", "8125583")

seed_wilson <- createLines(condition[c(1, 2, 3,4,7,8,9)], "wilson", "one", seed = TRUE) %>%
  noquote()
names(seed_wilson) <- c("8125584", "8125585", "8125586", "8125587", "8125588", "8125589", "8125590")
```

```{r}
seed_ptsd <- createLines(condition[c(1, 2, 3,4,7,8,9)], "ptsd", "one", seed = TRUE) %>%
  noquote()

# sctd later

seed_software <- createLines(condition[c(1, 2, 3,4,7,8,9)], "software", "one", seed = TRUE) %>%
  noquote()
# sctd later
names(seed_software) <- c("8129589", "8129732", "8129588", ".", ".", ".", ".")

# ptsd sctd
